Graph Product Structure for Non-Minor-Closed Classes

### 2021-11-19 slides/slides.tex
Small stuff

    \textbf{Claim:} $\tw(H')\le\binom{k+t}{t}-1$

    \textit{Proof:}
    \begin{itemize}
      \item Each $x\in V(H')$ is obtained by contracting $S_x$
      \item Use tree nice tree decomposition with the same tree $T$
      \item If $xz\in E(H')$ and $x\prec_T z$ then drag $x$ down into $B_z$
      \item Point: If $x\in B_{z'}$ then $x\prec_T z'\prec_T z$ and $\mathop{dist}_{H}(x,z)\le k$.  
      \item By Pilipczuk-Siebertz Lemma, $|B_{z'}|\le \binom{k+t}{t}$.
    \end{itemize}
\end{frame}

\begin{frame}
  \begin{itemize}
    \item each $S_x$ contains $O(1)$ vertices from each row of $H\boxtimes P$. (Easy, each vertex in $S_x$ from row $i$ comes from a shortcut through a vertex of $Y_x$ in row $i-1$, $i$, or $i+1$, so $3dk\ell(k+1)=3d\ell(k^2+k)$) 
  \end{itemize}
\end{frame}

>>>>

    \textbf{Claim:} $\tw(H')\le\binom{k+t}{t}-1$
    \vspace{1cm}
    \textit{Proof:}
    \begin{itemize}
      \item Each $x\in V(H')$ is obtained by contracting $S_x$
      \item Use tree nice tree decomposition with the same tree $T$
      \item If $xz\in E(H')$ and $x\prec_T z$ then drag $x$ down into $B_z$
      \item Point: If $x\in B_{z'}$ then $x\prec_T z'\prec_T z$ and $\mathop{dist}_{H}(x,z)\le k$.  
      \item By Pilipczuk-Siebertz Lemma, $|B_{z'}|\le \binom{k+t}{t}$.
    \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Thickness}

  \begin{itemize}
    \item Recall that $\mathcal{P'}$ is a $(k,dk\ell)$-shortcut system over $H\boxtimes P$.
    \item We can show that the subset of $H\boxtimes P\boxtimes K_{\ell}$ corresponding to $S_x$ contains at most $d\ell(k^2+3)$ vertices from each layer of $H\boxtimes P\boxtimes K_{\ell}$.
    \item Implies $G^{\mathcal{P}}\subseteq H'\boxtimes P\boxtimes K_{d\ell(k^2+3)}$
  \end{itemize}
\end{frame}
